Project

### 2022-04-03 Project/DraftR.Rmd
Update DraftR.Rmd

```{r}
library(ape)
library(tidyr)
library(MASS)
library(MuMIn)
library(ggplot2)
library(reshape2)
library(grid)
library(gridExtra)
library(ggfortify)
library(dplyr)

@@

```{r}
ltrsdat$year <- as.factor(ltrsdat$year)
ltrsdat$transect <- as.factor(ltrsdat$transect)
ltrsdat$site <- as.factor(ltrsdat$site)
ltrsdat$treat <- as.factor(ltrsdat$treat)
ltrsdat$Source <- as.factor(ltrsdat$Source)
ltrsdat$tbo <- as.factor(ltrsdat$tbo)
```

@@

# Group by Source
SourceListH <- gsub("\\w+\\s+(\\w+)\\s.*","\\1", ltrsH_tree$tip.label)
SourceGroupH <- split(ltrsH_tree$tip.label, SourceListH)
SourceTreeH <- groupOTU(ltrsH_tree, SourceGroupH)

# Create tree
ltrsHNJTree <- ggtree(SourceTreeH, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SourceGroupHBray <- split(ltrsHTree_bray$tip.label, SourceListH)
SourceTreeHBray <- groupOTU(ltrsHTree_bray, SourceGroupHBray)

# Create tree
ltrsHBrayTree <- ggtree(SourceTreeHBray, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SourceListM <- gsub("\\w+\\s+(\\w+)\\s.*","\\1", ltrsM_tree$tip.label)
SourceGroupM <- split(ltrsM_tree$tip.label, SourceListM)
SourceTreeM <- groupOTU(ltrsM_tree, SourceGroupM)

# Create tree
ltrsMNJTree <- ggtree(SourceTreeM, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SourceGroupMBray <- split(ltrsMTree_bray$tip.label, SourceListM)
SourceTreeMBray <- groupOTU(ltrsMTree_bray, SourceGroupMBray)

# Create tree
ltrsMBrayTree <- ggtree(SourceTreeMBray, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SourceListL <- gsub("\\w+\\s+(\\w+)\\s.*","\\1", ltrsL_tree$tip.label)
SourceGroupL <- split(ltrsL_tree$tip.label, SourceListL)
SourceTreeL <- groupOTU(ltrsL_tree, SourceGroupL)

# Create tree
ltrsLNJTree <- ggtree(SourceTreeL, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SourceGroupLBray <- split(ltrsLTree_bray$tip.label, SourceListL)
SourceTreeLBray <- groupOTU(ltrsLTree_bray, SourceGroupLBray)

# Create tree
ltrsLBrayTree <- ggtree(SourceTreeLBray, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

>>>>

```{r}
library(ape)
library(tidyr)
library(MASS)
library(MuMIn)
library(ggplot2)
library(reshape2)
library(grid)
library(gridExtra)
library(ggfortify)
library(vegan)
library(ggtree)
library(dplyr)

@@

```{r}
#ltrsdat$year <- as.factor(ltrsdat$year)
#ltrsdat$transect <- as.factor(ltrsdat$transect)
#ltrsdat$site <- as.factor(ltrsdat$site)
#ltrsdat$treat <- as.factor(ltrsdat$treat)
#ltrsdat$Source <- as.factor(ltrsdat$Source)
#ltrsdat$tbo <- as.factor(ltrsdat$tbo)
```

@@

# Group by Source
SiteListH <- gsub("\\w+\\s+(\\w+)\\s.*","\\1", ltrsH_tree$tip.label)
SiteGroupH <- split(ltrsH_tree$tip.label, SiteListH)
SiteTreeH <- groupOTU(ltrsH_tree, SiteGroupH)

# Create tree
ltrsHNJTree <- ggtree(SiteTreeH, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SiteGroupHBray <- split(ltrsHTree_bray$tip.label, SiteListH)
SiteTreeHBray <- groupOTU(ltrsHTree_bray, SiteGroupHBray)

# Create tree
ltrsHBrayTree <- ggtree(SiteTreeHBray, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SiteListM <- gsub("\\w+\\s+(\\w+)\\s.*","\\1", ltrsM_tree$tip.label)
SiteGroupM <- split(ltrsM_tree$tip.label, SiteListM)
SiteTreeM <- groupOTU(ltrsM_tree, SiteGroupM)

# Create tree
ltrsMNJTree <- ggtree(SiteTreeM, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SiteGroupMBray <- split(ltrsMTree_bray$tip.label, SiteListM)
SiteTreeMBray <- groupOTU(ltrsMTree_bray, SiteGroupMBray)

# Create tree
ltrsMBrayTree <- ggtree(SiteTreeMBray, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SiteListL <- gsub("\\w+\\s+(\\w+)\\s.*","\\1", ltrsL_tree$tip.label)
SiteGroupL <- split(ltrsL_tree$tip.label, SiteListL)
SiteTreeL <- groupOTU(ltrsL_tree, SiteGroupL)

# Create tree
ltrsLNJTree <- ggtree(SiteTreeL, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")

@@

# Group by Source
SiteGroupLBray <- split(ltrsLTree_bray$tip.label, SiteListL)
SiteTreeLBray <- groupOTU(ltrsLTree_bray, SiteGroupLBray)

# Create tree
ltrsLBrayTree <- ggtree(SiteTreeLBray, layout = "circular", aes(colour = group)) +
  geom_tiplab(size = 2, aes(angle = 0)) +
  theme(legend.position = "right")
